Gains and losses in rheumatoid arthritis data from inferCNV

### 2024-03-06 infercnv/reports/gains_and_losses.Rmd
change chisq to fisher exact in gains/losses statistical test

```{r fisher_exact}
chisq <- xfun::cache_rds({

  chisq <-
    colnames(sce@colData)[grepl('_gain$|_loss$', colnames(sce@colData))] %>%
    purrr::set_names() %>%
    purrr::map(function(event) {

      if (1 %in% cont[, event, drop = T]) {

        # run chi-squared test
        chisq <- chisq.test(sce@colData[, 'chr7_gain', drop = T], 
                            sce@colData[, event, drop = T])

         # return relevant stats
        tibble::tibble(
          X_squared = chisq$statistic, 
          p = chisq$p.value, 
          df = chisq$parameter['df'])

@@

    }) %>%
    dplyr::bind_rows(.id = 'event') %>%
    # remove chr7+
    dplyr::filter(event != 'chr7_gain') %>%
    dplyr::arrange(p)

  # return
  chisq

}, file = 'chisq.rds', rerun = params$rerun)

chisq %>%
  knitr::kable()
```

>>>>

```{r fisher_exact}
fisher <- xfun::cache_rds({

  fisher <-
    colnames(sce@colData)[grepl('_gain$|_loss$', colnames(sce@colData))] %>%
    purrr::set_names() %>%
    purrr::map(function(event) {

      event_vec <- sce@colData[, event, drop = T]

      if (1 %in% event_vec) {

        # run fisher exact test
        fisher <- fisher.test(sce$chr7_gain, event_vec)

         # return relevant stats
        tibble::tibble(
          OR = fisher$estimate, 
          p = fisher$p.value)

      } else {

        # no event
        tibble::tibble(OR = NA, p = NA)

@@

    }) %>%
    dplyr::bind_rows(.id = 'event') %>%
    # remove chr7+ (can't do chr7+ vs chr7+)
    dplyr::filter(event != 'chr7_gain') %>%
    dplyr::arrange(-OR)

  # return
  fisher

}, file = 'fisher.rds', rerun = params$rerun)

fisher %>%
  knitr::kable()
```
